Approximation as Differentiation notes

### 2025-02-09 notes.tex
Fam(I,C) is a functor category where the naturality conditions are trivial because I is discrete.
Reindexing.
Reindexing functor.

\noindent Suppose $x \in \Fam(I,C)$ and $y \in \Fam(J,C)$. Define $y_f$ for any $f: I \to J$ to be the
$I$-indexed family of objects of $C$.

@@

In our code we give a slightly different construction. For a category $C$, define the category where:
\begin{itemize}
\item objects are pairs $(I, x)$ with $I$ a set and $x$ an $I$-indexed family of objects of $C$
\item morphisms from $(I, x)$ to $(J, y)$ are functions $f: I \to J$ paired with morphisms
\end{itemize}

>>>>

\begin{definition}[Reindexing functor]
For any $X \in \Fam(J,C)$ and $f: I \to J$ define $X[f] \in \Fam(I,C)$ where $X[f]_i = X_{fi}$.
\end{definition}

[$\Fam(-,C)$ is a fibred category over $\Set$?]

@@

In our code we give a slightly different construction. For a category $C$, define the category where:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and indexed family $X$ in $\Fam(I,C)$
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with morphisms $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}
